\section{Example 2}
You can find this example in this directory but renamed to \textit{MLP9\_1\_1.m\_template}.
I will explain only differencies to the example1, so please read it first, if you haven't.

\subsection{Introduction}
Our problem can be solved with a monotonically increasing or decreasing surface. An input vector \textbf{p}
(with 9 values) should be mapped onto one output value.
Because we know that it can be solved with a monotonically increasing or decreasing surface,
we can choose a 9-1-1 multi-layer perceptron (short: MLP).
This means an MLP with 9 input neurons, only 1 hidden neuron and with 1 output neuron.

\subsection{Code m-file}
\input{examples/2/MLP9_1_1}

\subsection{Walkthrough}
The difference to the example1 starts below the line number 0035.\\
The difference concerns only the pre-processing section where the data set is splittet into 
the three subsets. This time, the command \textbf{subset} is used, which makes the complete
example about 19 lines shorter!
On line 0023 \& 0024 data will be loaded. This data matrix contains 13 columns.
Column 4, 8 and 12 won't be used (this is because the datas are of a real world problem).
Column 13 contains the target values.\\

Now on line 35 we have to merge the input and output targets again. Subset will take the complete
matrix as argument! On line 42 happens the complete magic :-). Subset will return three 
subsets containing each time the input and output arguments. So this part must be splitet once more!
But this is very easy and happens at some specific positions below.\\

That's it, \textbf{subset} will help you to write short scripts!




